Analysis on Movie Success Indicators

### 2024-04-02 paper/paper.qmd
For peer eval

---
title: "Analysis on Movie Success Indicators"
author: 
  - Qi Er (Emma) Teng
thanks: "Code and data are available at: https://github.com/dwz92/Analysis-on-Movie-Success-Indicators."
date: today
date-format: long
abstract: "In this study, we delve into the variables contributing to movie success, focusing on the interplay between a movies’ genre, number of theaters showing, the moth of release, and the year of premiere, particularly in the context of the pre and post-COVID-19 era, spanning from 2019 to 2022. This comprehensive analysis aims to shed light on the nuanced relationship between these variables and movie success, highlighting how the cinematic landscape has evolved in response to the COVID-19 pandemic. The findings of this study enrich our understanding of the determinants of cinematic success, providing valuable insights for filmmakers, distributors, and industry strategists in navigating the changing film industry."
format: html
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

Talk way more about it.

@@

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

@@

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

Our results are summarized in @tbl-modelresults.

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Weaknesses and next steps should also be included.

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@@

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

---
title: "Analysis on Movie Success Indicators"
author: 
  - Qi Er (Emma) Teng
thanks: "Code and data are available at: https://github.com/dwz92/Analysis-on-Movie-Success-Indicators."
date: today
date-format: long
abstract: "In this study, we delve into the variables contributing to movie success, focusing on the interplay between a movies’ genre, number of theaters showing, the moth of release, and the year of premiere, particularly in the context of the pre and post-COVID-19 era, spanning from 2019 to 2022. This comprehensive analysis aims to shed light on the nuanced relationship between these variables and movie success, highlighting how the cinematic landscape has evolved in response to the COVID-19 pandemic. The findings of this study enrich our understanding of the determinants of cinematic success, providing valuable insights for filmmakers, distributors, and industry strategists in navigating the changing film industry."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

In the realm of global entertainment, movies hold a pivotal role, not only as a form of artistic expression but also as a significant driver of cultural and economic activity. The advent of COVID-19 has precipitated profound changes across the global media landscape, altering audience behaviors and consumption patterns. The surge in online media consumption during the pandemic has brought unprecedented challenges and transformations to the traditional movie industry. This shift has prompted a reevaluation of what factors contribute to a movie's success in an era where digital platforms are increasingly dominating. Against this backdrop, this paper aims to analyze several indicators related to movie success, taking into account the impact of COVID-19 on both the production and consumption of films. By examining the interplay between various factors and movie ratings, this study seeks to uncover insights into the dynamics of movie success in a rapidly evolving media environment.

Employing a multifaceted analytical approach that combines genre classification, theaters metrics, seasonal release timing, and annual trends, we probed the determinants of cinematic success in the fluctuating entertainment landscape from 2019 to 2022. Our study meticulously compiled data from Box Office Mojo and IMDb, focusing on films that achieved a commendable rating of 7/10 or above, signifying both critical and popular acclaim. Through the application of advanced statistical techniques and web scraping tools, we dissected the top 200 grossing films to unravel the intricate relationship between these variables and their collective impact on a movie's success. A higher performance in these metrics typically correlates with a movie's ability to resonate with diverse audiences, navigate distribution challenges, and capitalize on favorable release windows. This analysis not only sheds light on the evolving criteria for what makes a movie successful in the digital age but also offers insights into the strategic considerations filmmakers and distributors must weigh in an increasingly competitive and segmented market.

The paper is structured to facilitate a comprehensive understanding of the study and its implications. Following Section 1, Section 2 presents the data, detailing the data sources, analytical techniques, and the rationale behind the chosen methods. Section 4 discusses the results. Section 5 provides an in-depth discussion of these findings.

@@

//TODO

@@

// TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

//TODO

@@

## Diagnostics
//TODO
